### 2022-01-26 README.Rmd
PLB COMMENTS ADDRESSED

We recognize that the species and ecosystems studied in this paper are within
the traditional range of the Inpuiaq and Yupik people. And, we would like to
acknowledge and thank them as the original stewards of these ecosystems. The
deployment of bio-logging devices used in this study were often done in
collaboration with Alaska Native seal hunters near their communities. We would
like to especially acknowledge the communities of Kotzebue, Koyuk, Nome,
Nuiqsut, Scammon Bay, St. Michael, Utqiaġvik, and Ulguniq (Wainwright) and the
following individuals: James Adams, Jeff Barger, David Barr, Wendell Booth,
Cyrus Harris, Nereus 'Doc' Harris, Grover Harris, Lee Harris, Tom Jones, Frank
Garfield, Brenda Goodwin, Henry Goodwin, John Goodwin, Pearl Goodwin, Willie
Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr., Virgil Naylor Sr., Dan
Savetilik, Chuck Schaeffer, Ross Schaeffer, Allen Stone, and Randy Toshavik from
Kotzebue, Alaska; Merlin Henry from Koyuk, Alaska; Tom Gray from Nome; Vernon
Long and Richard Tukle from Nuiqsuit, Alaska; Morgan Simon, River Simon, and Al
Smith from Scammon Bay, Alaska; Alex Niksik Jr. from St. Michael, Alaska; Billy
Adams, James Aiken, Tim Aiken, Howard Kittick, Gilbert Leavitt, Isaac Leavitt,
J.R. Leavitt, and Joe Skin from Utqiaġvik, Alaska; Mary Ellen Ahmaogak, Enoch
Oktollik, Shawn Oktollik, Stacey Osborn, and Fred Rexford from Ulguniq, Alaska.

>>>>

We recognize that the species and ecosystems we studied are within the ancestral
and present-day environs of the Inupiat and Yup'ik people who, through many
uncredited contributions of traditional knowledge, provided early western
naturalists and scientists with much of what gets described as the ‘basic
biology’ of Arctic seals. The deployment of bio-logging devices used in this
study were often done in collaboration with Alaska Native seal hunters near
their communities. We would like to especially acknowledge the communities of
Kotzebue, Koyuk, Nome, Nuiqsut, Scammon Bay, St. Michael, Utqiaġvik, and Ulguniq
(Wainwright) and the following individuals: James Adams, Jeff Barger, David
Barr, Wendell Booth, Cyrus Harris, Nereus 'Doc' Harris, Grover Harris, Lee
Harris, Tom Jones, Frank Garfield, Brenda Goodwin, Henry Goodwin, John Goodwin,
Pearl Goodwin, Willie Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr.,
Virgil Naylor Sr., Dan Savetilik, Chuck Schaeffer, Ross Schaeffer, Allen Stone,
and Randy Toshavik from Kotzebue, Alaska; Merlin Henry from Koyuk, Alaska; Tom
Gray from Nome; Vernon Long and Richard Tukle from Nuiqsuit, Alaska; Morgan
Simon, River Simon, and Al Smith from Scammon Bay, Alaska; Alex Niksik Jr. from
St. Michael, Alaska; Billy Adams, James Aiken, Tim Aiken, Howard Kittick,
Gilbert Leavitt, Isaac Leavitt, J.R. Leavitt, and Joe Skin from Utqiaġvik,
Alaska; Mary Ellen Ahmaogak, Enoch Oktollik, Shawn Oktollik, Stacey Osborn, and
Fred Rexford from Ulguniq, Alaska.
